Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-11 paper.tex
Minor edits

\note{Tristan}{Vocabulary (check consistency across the paper): tool vs. application}
\note{Tristan}{Targeted journals: Scientific Data, Giga Science, Frontiers in Neuroinformatics, Future Generation Computer Systems}

@@

\subsection{Parallelization support}
\label{sec:parallelization}
\boutiques supports parallelism by allowing applications to submit new
invocations through the following protocol \todo{Needs to be
  documented on Github}:
\begin{enumerate}
\item Applications write a JSON object complying to the invocation
  schema in their execution directory.
\item The platform reads the JSON object, creates the corresponding
  invocation, and writes back the invocation id in the same directory.
% The platform could also support status requests.
\end{enumerate}
Several invocations can be submitted at once, possibly using the
\texttt{task-dependencies} array to specify dependencies among
them. This mechanism is implemented in the Boutiques schema using a
single property, \texttt{can-submit-tasks}.

@@

\section{Acknowledgments}

Amazon grant.

>>>>

%\note{Tristan}{Vocabulary (check consistency across the paper): tool vs. application}
%\note{Tristan}{Targeted journals: Scientific Data, Giga Science, Frontiers in Neuroinformatics, Future Generation Computer Systems}

@@

\subsection{Parallelization support}
\label{sec:parallelization}
\boutiques supports parallelism by allowing applications to submit new
invocations through \notimplementedyet{the following protocol}:
\begin{enumerate}
\item Applications write a JSON object complying to the invocation
  schema in their execution directory.
\item The platform reads the JSON object, creates the corresponding
  invocation, and writes back the invocation id in the same directory.
% The platform could also support status requests.
\end{enumerate}
Several invocations can be submitted at once, possibly using the
\texttt{task-dependencies} array to specify dependencies among
them. This mechanism is implemented in the Boutiques schema using a
single property, \texttt{can-submit-tasks}.

@@
